# Racism Detection in Dutch with R

Racism Detection in Dutch with R based on the CLiPS HAte speech DEtection System dataset. The dataset provides a dictionary of racist language used in Dutch, provided under the [CC BY-SA 4.0](https://creativecommons.org/licenses/by-sa/4.0/) license.

- The  **hatespeech.dutch** package provides the dataset in R format and provides R functions to easily work detect racism in the Dutch language. 

- The package allows to **detect the 16 categories of hatespeech**: 
Neutral-Country, Neutral-Migration, Neutral-Nationality, Neutral-Religion, Neutral-Skin_color, Racist-Animals, Racist-Country, Racist-Crime, Racist-Culture, Racist-Diseases, Racist-Migration, Racist-Nationality, Racist-Race, Racist-Religion, Racist-Skin_color, Racist-Stereotypes

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = "")
```

## Example

```{r}
library(hatespeech.dutch)
library(tau)
racismtypes <- racism_detector(type = "expanded")

x <- "Kan je niets aan doen dat je behoort tot het ras dat nog minder verstand en gevoelens heeft in uw hersenen dan het stinkend gat van een VARKEN ! :-p"
detect_hatespeech(x, detector = racismtypes)
```

```{r}
library(hatespeech.dutch)
library(udpipe)
x <- "Omdat SF het woord hoer vaak benoemt, heb ik er maar halal hoer van gemaakt :zozo: Ik vond 'hoer zo onbeschoft om te benoemen, dus wat verzacht met halal..
Halal hoer bestaat toch niet? :vreemd:"
detection <- detect_hatespeech(x, detector = racismtypes, type = "udpipe", detailed = TRUE)
detection[, c("token", "lemma", "Racist-Culture", "Racist-Religion", "Racist-Skin_color")]
```

## How does this work?

A tokeniser (tau R package or udpipe R package) tokenises the full text in words. The `detect_hatespeech` function next looks for each word or lemma of the word if it is part of the racismtypes dictionary or it looks if it finds a more complex regular expression in the tokenised data.
An example dictionary for racist-religion looks as follows:

```{r}
racismtypes[["Racist-Religion"]]
```

## Installation

```{r, eval=FALSE}
install.packages("tau")
devtools::install_github("bnosac/udpipe")
devtools::install_github("weRbelgium/hatespeech.dutch")
```

## Notes on CC BY-SA 4.0

The original data in the hatespeech.dutch R package is provided at  https://github.com/clips/hades.
Importing this data in R has been done based on the scripts available at the inst/dev directory.

## Support in text mining

Need support in text mining. 
Contact BNOSAC: http://www.bnosac.be

